Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-12 xrb2/paper.tex
section 3.1 clarifcation in blue

The {\tt F500} and {\tt F1000} runs both qualitatively resemble the flame structure in 
\citet{flame_wave1} --- a laterally propagating flame that is lifted off of the bottom of the fuel 
layer --- but they differ in their burning structures. Figures~\ref{fig:time_series_500} and 
\ref{fig:time_series_1000} show time series of the mean molecular weight, $\bar{A}$, for the {\tt 
F500} and {\tt F1000} runs.  Compared to those in \cite{flame_wave1}, ashes behind the flame do not 
reach as high atomic weights. This is not surprising, since those previous runs artificially 
boosted the reaction rates.  Comparing these two new runs, the burning is much more evolved for the 
higher rotation rate, and the ash is actually able to move ahead of the flame front (visible in the 
Figure  \ref{fig:time_series_1000} $100~\mathrm{ms}$ snapshot). We believe that this is because the increased 
rotation better confines the initial perturbation and subsequent expansion from the burning, 
increasing the temperature and density in the flame front such that the reaction rate increases, 
which allows the reactions to progress further. {\color{blue} The $\dot{e}_\mathrm{nuc}$ plots in Figure \ref{fig:time_series_enuc_1000} also support this interpretation, with the interior\MarginPar{What is meant by interior here?? The edge? The part nearest the crust?} of the {\tt F1000} flame reaching higher $\dot{e}_\mathrm{nuc}$ values than for the {\tt F500} run in Figure \ref{fig:time_series_enuc_500}.} In contrast to {\tt F500} and {\tt F1000}, the 
lowest rotation run --- {\tt F250} --- failed to ignite. The lack of ignition for {\tt F250} also 
aligns with the reasoning given above, with the lower rotation in this case potentially leading to 
insufficient confinement such that the temperature and density required for ignition is not 
achieved. In this scenario, another source of confinement (e.g.\ magnetic fields) would need to 
take over at lower rotation rates to allow a burst to occur, at least for the initial model used 
here.

>>>>

The {\tt F500} and {\tt F1000} runs both qualitatively resemble the flame structure in 
\citet{flame_wave1} --- a laterally propagating flame that is lifted off of the bottom of the fuel 
layer --- but they differ in their burning structures. Figures~\ref{fig:time_series_500} and 
\ref{fig:time_series_1000} show time series of the mean molecular weight, $\bar{A}$, for the {\tt 
F500} and {\tt F1000} runs.  Compared to those in \cite{flame_wave1}, ashes behind the flame do not 
reach as high atomic weights. This is not surprising, since those previous runs artificially 
boosted the reaction rates.  Comparing these two new runs, the burning is much more evolved for the 
higher rotation rate, and the ash is actually able to move ahead of the flame front (visible in the 
Figure  \ref{fig:time_series_1000} $100~\mathrm{ms}$ snapshot). We believe that this is because the increased 
rotation better confines the initial perturbation and subsequent expansion from the burning, 
increasing the temperature and density in the flame front such that the reaction rate increases, 
which allows the reactions to progress further. {\color{blue} The $\dot{e}_\mathrm{nuc}$ plots in Figure \ref{fig:time_series_enuc_1000} also support this interpretation, with the interior of the flame nearest to the crust\MarginPar{What is meant by interior here?? The edge? The part nearest the crust?} in the {\tt F1000} run reaching higher $\dot{e}_\mathrm{nuc}$ values than for the {\tt F500} run in Figure \ref{fig:time_series_enuc_500}.} In contrast to {\tt F500} and {\tt F1000}, the 
lowest rotation run --- {\tt F250} --- failed to ignite. The lack of ignition for {\tt F250} also 
aligns with the reasoning given above, with the lower rotation in this case potentially leading to 
insufficient confinement such that the temperature and density required for ignition is not 
achieved. In this scenario, another source of confinement (e.g.\ magnetic fields) would need to 
take over at lower rotation rates to allow a burst to occur, at least for the initial model used 
here.
